``How Prolific Are You?": A Scientometric Analysis of Researchers

### 2018-11-30 paper/paper.tex
Added note on feature scaling

>>>>

We did not scale the features before clustering, because the distributions of all the features were different (running a Kolgomorov-Smirnov test on every pair of features gave p-values < 0.05). To prove that feature scaling is an incorrect step empirically, we performed both z-standardization and feature scaling to [0, 100]. In both cases, we found the value of \textit{eps} in the same way discussed above, but starting from 0.001 and going in increments of 0.001. In both cases, DBSCAN returned 60 individual clusters, and one other cluster containing all the points.
